---
title: "Create Figure 2"
author: "Lauren Zamora"
format: html
editor: visual
---

## Figure 2

This figure shows properties over summertime sea ice of single-layer clouds at least partially overlapping with 2.5-3.5 km elevation, from May to September. a, b) Estimated average cooling from cloud changes due to dust aerosols (-dCREboa and -dCREtoa, respectively). Error bars show the vales at the low- and high-end FLEXPART background dust threshold. c) The average FLEXPART (black) and MERRA-2 (orange) dust concentrations associated with the clouds. d) Average % of time that the clouds were at temperatures below -10 °C. e) The average solar zenith angle for the clouds at the time of measurement.

## Running Code

For **Figure 2** first load the following libraries:

```{r}
library(ggplot2)
library(gridExtra)
library(dplyr)
library(ggpubr)
```

Load the data:

```{r}
boatoa<-read.csv(file="../../data/derived_data/fig2.csv")
setDT(boatoa)
databoa<-boatoa[level=="BOA"]
datatoa<-boatoa[level=="TOA"]
```

Create the plot:

```{r}
#So R doesn't alphabetically order the data
ppal <- c(
  "May" = databoa$color[1],
  "Jun" = databoa$color[2], 
  "Jul" = databoa$color[3], 
  "Aug" = databoa$color[4],
  "Sep" = databoa$color[5] 
)

coeff_dust <- 10

jpeg(file='../../figures/Figure2.jpeg', width=65, height=200, units='mm', res=600)

p1<-ggplot(databoa) + geom_bar( aes(x=numeric_month, y=dCRE), stat="identity", fill="skyblue", alpha=0.7)  + theme(axis.title.y=element_text(size=8), axis.title.x=element_text(size=8), panel.background = element_rect(fill = 'white', colour = 'black')) + geom_hline(yintercept=0, col="grey") + geom_errorbar( aes(x=numeric_month, ymin=dCRElo, ymax=dCREhi), width=0.2, colour="grey20", alpha=0.9, size=0.8)+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + labs(x = "Month \n", y = expression("-\u{2202}CRE, W m"^-2)) + annotate("text", x=7, y=15, label= "BOA", size=4) + annotate("text", x = 8.5, y = 16, label = 'bold("a)")', parse = TRUE)

p2<-ggplot(datatoa) + geom_bar( aes(x=numeric_month, y=dCRE), stat="identity", fill="skyblue", alpha=0.7) + theme(axis.title.y=element_text(size=8), axis.title.x=element_text(size=8), panel.background = element_rect(fill = 'white', colour = 'black'))+ geom_errorbar( aes(x=numeric_month, ymin=dCRElo, ymax=dCREhi), width=0.2, colour="grey20", alpha=0.9, size=0.8) + labs(x = "Month \n", y = expression("-\u{2202}CRE, W m"^-2)) + theme(axis.title.y=element_text(angle=90, vjust=1)) +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + geom_hline(yintercept=0, col="grey")  +
   lims(y=c(-3,18), x=c(4.5,9.5))  +
   annotate("text", x=7, y=15, label= "TOA", size=4) +
   annotate("text", x = 8.5, y = 16, label = 'bold("b)")', parse = TRUE) 

p3<- ggplot(databoa) + geom_line(aes(x = numeric_month, y = mean_fdust), col="black",lty=1) + theme(axis.title.y=element_text(size=8), axis.title.x=element_text(size=8), panel.background = element_rect(fill = 'white', colour = 'black'))+ labs(x = "Month", y = expression("Mean FLEXPART dust, ng m"^-3)) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.ticks.y = element_line(color = "black"), axis.text.y = element_text(color = "black"), axis.title.y = element_text(color = "black"), axis.line.y = element_line(color = "black"))  + lims(y=c(50,400), x=c(4.5,9.5)) +
   annotate("text", x = 8.5, y = 360, label = 'bold("c)")', parse = TRUE) + geom_line(aes(x = numeric_month, y = mean_mdust/coeff_dust), col="orangered",lty=1) + scale_y_continuous(name = expression("Mean FLEXPART dust, ng m"^-3), sec.axis = sec_axis(~.*coeff_dust, name=expression("Mean MERRA-2 dust, ng m"^-3) )) + theme( axis.title.y = element_text(color = "black", size=8), axis.title.y.right = element_text(color = "orangered", size=8), axis.ticks.y.right = element_line(color = "orangered"), axis.line.y.right = element_line(color = "orangered"), axis.text.y.right = element_text(color = "orangered")) 

p4<- ggplot(databoa) + geom_line(aes(x = numeric_month, y = frac_ltn10), col="deepskyblue3",lty=1) + theme(axis.title.y=element_text(size=8), axis.title.x=element_text(size=8), panel.background = element_rect(fill = 'white', colour = 'black'))+ labs(x = "Month", y = expression("% time T < -10 "*degree*C)) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.ticks.y = element_line(color = "deepskyblue3"), axis.text.y = element_text(color = "deepskyblue3"), axis.title.y = element_text(color = "deepskyblue3"), axis.line.y = element_line(color = "deepskyblue3")) +lims(y=c(0,100), x=c(4.5,9.5)) +
   annotate("text", x = 8.5, y = 95, label = 'bold("d)")', parse = TRUE)

p5<- ggplot(databoa) + geom_line(aes(x = numeric_month, y = sza), col="darkgreen",lty=1) + theme(axis.title.y=element_text(size=8), axis.title.x=element_text(size=8), panel.background = element_rect(fill = 'white', colour = 'black'))+ labs(x = "Month", y = "Solar zenith angle") +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.ticks.y = element_line(color = "darkgreen"), axis.text.y = element_text(color = "darkgreen"), axis.title.y = element_text(color = "darkgreen"), axis.line.y = element_line(color = "darkgreen")) +lims(y=c(0,90), x=c(4.5,9.5)) +
   annotate("text", x = 8.5, y = 85, label = 'bold("e)")', parse = TRUE)

ggarrange(p1,p2,p3, p4,p5,ncol=1, widths=c(2,1), heights=1, align="v")



dev.off()
```
