---
title: "figureS4"
author: "Lauren Zamora"
format: html
editor: visual
---

## Figure S4

This figure shows the within i, j bin relationships between del_glaciation and del\_(MERRA-2 dust) and del\_(MERRA-2 SO4).

## Running Code

For **Figure S4** first load the following libraries:

```{r}
library(hexbin)
library(RColorBrewer)
library(mgcv)
library(dplyr)
library(ggplot2)
library(data.table)
library(ggpubr)
```

Load the tog data set, which represents the output of the GAM, and deviance predicted by each variable, and the tog2 data set, which is the same, except for MERRA-2 temperatures below -10 degrees C:

```{r}
tog<-read.csv("../../data/derived_data/tog.csv")
tog<-read.csv("../../data/derived_data/tog2.csv")
```

Add how many samples were in the top 10 most common meteorological bins, and the average T and Qv conditions of the bin. Where the MERRA-2 and AIRS T bins differ, take the average of the two.

```{r}
n<-c(614761, 472400 ,389737 ,355275 , 349762 , 274645 , 205167 , 200945 , 161074 ,154076)
meanT<-c( -13.75+1.875, -17.5+1.875,-21.25+1.875,  -10+1.875, -10+1.875, -17.5+1.875,    -13.75+1.875,    -25+1.875,   -13.75+1.875, mean(c(-17.5+1.875, -13.75+1.875) ))
meanQV<-c(0.001+0.0005, 0.001+0.0005, 0+0.0005, 0.002+0.0005, 0.001+0.0005 , 0+0.0005 , 0+0.0005 , 0+0.0005 , 0.002+0.0005 , 0.001+0.0005 )


```

Plot all the information from each i,j bin together, along with sample number:

```{r}

dglaciation<-tog$dglaciation
dmerdust<-tog$dmerdust
dSO4<-tog$dSO4
final<-data.frame(dglaciation, dmerdust, dSO4)

pdust<-ggplot(final, aes(x = dmerdust, y = dglaciation)) +   stat_binhex() +   scale_fill_gradient(name = "count", trans = "log",  breaks = 10^(0:2)) + theme(axis.title.y=element_text(size=8), axis.title.x=element_text(size=8), panel.background = element_rect(fill = 'white', colour = 'black')) + labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 dust)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') )))) + lims(y=c(-25,50), x=c(-2500,3000)) 

pso4<-ggplot(final, aes(x = dSO4, y = dglaciation)) +   stat_binhex() +   scale_fill_gradient(name = "count", trans = "log",  breaks = 10^(0:2)) + theme(axis.title.y=element_text(size=8), axis.title.x=element_text(size=8), panel.background = element_rect(fill = 'white', colour = 'black')) + labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 sulfate)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') )))) + lims(y=c(-25,50), x=c(-300,400)) 




dglaciation<-tog2$dglaciation
dmerdust<-tog2$dmerdust
dSO4<-tog2$dSO4
final2<-data.frame(dglaciation, dmerdust, dSO4)

pdust2<-ggplot(final2, aes(x = dmerdust, y = dglaciation)) +   stat_binhex() +   scale_fill_gradient(name = "count", trans = "log",  breaks = 10^(0:2)) + theme(axis.title.y=element_text(size=8), axis.title.x=element_text(size=8), panel.background = element_rect(fill = 'white', colour = 'black')) + labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 dust)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') )))) + lims(y=c(-25,50), x=c(-2500,3000)) + annotate("text", x=-1500, y=45, label= expression(paste("T < -10 ",degree~C," ")), size=4)

pso42<-ggplot(final2, aes(x = dSO4, y = dglaciation)) +   stat_binhex() +   scale_fill_gradient(name = "count", trans = "log",  breaks = 10^(0:2)) + theme(axis.title.y=element_text(size=8), axis.title.x=element_text(size=8), panel.background = element_rect(fill = 'white', colour = 'black')) + labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 sulfate)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') )))) + lims(y=c(-25,50), x=c(-300,400)) + annotate("text", x=-150, y=45, label= expression(paste("T < -10 ",degree~C," ")), size=4)


jpeg(file='../../figures/FigureS5.jpeg',width=190, height=130, units='mm', res=600, pointsize=10)

ggarrange(pdust,pso4, pdust2,pso42, ncol=2, nrow=2, heights=1, align="v")

dev.off()
```

Plot the relationships in the top 10 most common meteorological bins for both MERRA-2 dust and sulfate variables:

```{r}
setDT(tog)
for(i in 1:10){
  eval(parse(t=paste0('tog',i,'<-tog[jbin==',i,']')))
}  
  jbin1dust <- ggplot(tog1, aes(x=dmerdust, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-2500,3000)) + labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 dust)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') )))) + annotate("text", x=-1500, y=30, label= "n=6M\navT=-11.9\navQv=0.0015", size=3)
  
    jbin2dust <- ggplot(tog2, aes(x=dmerdust, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-2500,3000)) + labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 dust)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') )))) + annotate("text", x=-1500, y=30, label= "n=5M\navT=-15.6\navQv=0.0015", size=3)
    
    jbin3dust <- ggplot(tog3, aes(x=dmerdust, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-2500,3000)) + labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 dust)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') ))))  + annotate("text", x=-1500, y=30, label= "n=4M\navT=-19.4\navQv=0.0005", size=3)
      
    jbin4dust <- ggplot(tog4, aes(x=dmerdust, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-2500,3000)) + labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 dust)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') ))))  + annotate("text", x=-1500, y=30, label= "n=4M\navT=-8.1\navQv=0.0025", size=3)
      
    jbin5dust <- ggplot(tog5, aes(x=dmerdust, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-2500,3000)) + labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 dust)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') )))) + annotate("text", x=-1500, y=30, label= "n=3M\navT=-8.1\navQv=0.0015", size=3)
      
    jbin6dust <- ggplot(tog6, aes(x=dmerdust, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-2500,3000)) + labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 dust)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') ))))  + annotate("text", x=-1500, y=30, label= "n=3M\navT=-15.6\navQv=0.0005", size=3)
      
    jbin7dust <- ggplot(tog7, aes(x=dmerdust, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-2500,3000)) + labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 dust)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') ))))  + annotate("text", x=-1500, y=30, label= "n=2M\navT=-11.9\navQv=0.0005", size=3)
      
    jbin8dust <- ggplot(tog8, aes(x=dmerdust, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-2500,3000)) + labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 dust)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') ))))  + annotate("text", x=-1500, y=30, label= "n=2M\navT=-23.1\navQv=0.0005", size=3)
      
    jbin9dust <- ggplot(tog9, aes(x=dmerdust, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-2500,3000)) + labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 dust)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') )))) + annotate("text", x=-1500, y=30, label= "n=2M\navT=-11.9\navQv=0.0025", size=3)
      
    jbin10dust <- ggplot(tog10, aes(x=dmerdust, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-2500,3000)) + labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 dust)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') ))))  + annotate("text", x=-1500, y=30, label= "n=2M\navT=-13.8\navQv=0.0015", size=3)
    
    jbin1SO4 <- ggplot(tog1, aes(x=dSO4, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-300,400))+ labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 sulfate)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') ))))
    
      jbin2SO4 <- ggplot(tog2, aes(x=dSO4, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-300,400))+ labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 sulfate)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') ))))
    
    jbin3SO4 <- ggplot(tog3, aes(x=dSO4, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-300,400))+ labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 sulfate)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') ))))
      
    jbin4SO4 <- ggplot(tog4, aes(x=dSO4, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-300,400))+ labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 sulfate)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') ))))
      
    jbin5SO4 <- ggplot(tog5, aes(x=dSO4, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-300,400))+ labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 sulfate)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') ))))
      
    jbin6SO4 <- ggplot(tog6, aes(x=dSO4, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-300,400))+ labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 sulfate)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') ))))
      
    jbin7SO4 <- ggplot(tog7, aes(x=dSO4, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-300,400))+ labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 sulfate)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') ))))
      
    jbin8SO4 <- ggplot(tog8, aes(x=dSO4, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-300,400))+ labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 sulfate)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') ))))
      
    jbin9SO4 <- ggplot(tog9, aes(x=dSO4, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-300,400))+ labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 sulfate)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') ))))
      
    jbin10SO4 <- ggplot(tog10, aes(x=dSO4, y=dglaciation)) + geom_point() + lims(y=c(-25,50), x=c(-300,400))+ labs(x = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}(MERRA-2 sulfate)'['i,j']*' (ng m'^-3*')') ))), y = expression(atop(NA, atop(textstyle(' '),textstyle('\u{2202}glaciation'['i,j']*' (%)') ))))

    
jpeg(file='../../figures/FigureS4.jpeg',width=190, height=1650/3, units='mm', res=600, pointsize=10)

ggarrange(jbin1dust, jbin1SO4,jbin2dust, jbin2SO4, jbin3dust, jbin3SO4, jbin4dust, jbin4SO4, jbin5dust, jbin5SO4, jbin6dust, jbin6SO4, jbin7dust, jbin7SO4, jbin8dust, jbin8SO4, jbin9dust, jbin9SO4, jbin10dust, jbin10SO4, ncol=2, nrow=10, heights=1, align="v")

dev.off()
```

Plot it all together:

```{r}

```
